---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 1"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Wesley James Williams"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, South Africa" # First Author's Affiliation
Email1: "21691126\\@sun.ac.za" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Financial Econometrics 871"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 12pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Answers the Question
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(xts)
library(tbl2xts)
library(RiskPortfolios)
library(PerformanceAnalytics)
library(PortfolioAnalytics)
library(lubridate)
library(kableExtra)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

MAA <- read_rds("data/MAA.rds")
msci <-
read_rds("data/msci.rds") %>%
filter(Name %in% c("MSCI_ACWI", "MSCI_USA", "MSCI_RE", "MSCI_Jap"))

```
<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Porfolio Construction
I present porfolios constructed with different risk metrics that abide by the following constraint

\begin{itemize}
\item Long-only strategy;
\itemWhen using covariance and mean forecasts, use a look-back of less than 3 years;
\item Do not hold any assets with less than 3 years’ returns data;
\item Apply Quarterly Rebalancing;
\item Limit exposure to Bonds and credit instruments at 25%;
\item Limit exposure to Equities at 60%;
\item Limit single asset exposure at 40%;
\item Data after 2010.
\end{itemize}
```{r}

#Now I combine the data frame
df_full <- rbind(msci %>%  rename("Tickers"= "Name"),MAA %>% select(-Name) %>% rename("Tickers" = "Ticker")) %>% 
    arrange(date) #sanity

#now lets clean the data according to the constraints
monthly_df <- df_full %>% 
  filter(date >= lubridate::ymd(20110101)) %>% # Only include data after 2010
  filter(n_distinct(format(date, "%Y")) >= 3) %>%  # Make sure that there is at least three years of data
  mutate(YM = format(date, "%Y%B")) %>% 
arrange(date) %>% 
group_by(Tickers, YM) %>% filter(date == last(date)) %>% 
group_by(Tickers) %>% 
mutate(ret = Price/lag(Price) - 1) %>% select(date, Tickers, 
    ret) %>% ungroup() %>% 
    filter(date > first(date))
```

```{r}
#now we need to get the return matrix to get Sigma and mu
#Following the extra tut, just to be careful lets make sure there are no missing values 
return_mat <- monthly_df %>% 
    spread(Tickers, ret)

# impute_missing_returns(return_mat, impute_returns_method = "NONE")
#Now that I know we do not have any NAs we can continue
return_mat_Nodate <- data.matrix(return_mat[, -1])
# Simple Sample covariance and mean:
Sigma <- RiskPortfolios::covEstimation(return_mat_Nodate)
Mu <- return_mat %>% summarise(across(-date, ~prod(1+.)^(1/n())-1)) %>% purrr::as_vector()


#Now need to make the amat and bvec
#1, currency 2. commodity 3. Currency 4. Bonds 5. bonds 6.Bonds 7. bonds 8. bonds 9. bonds 10. equity 11. equity 12. equity 13. equity: bonds (25%) 3:9 equity (60%) 10:13 UB 40%

# Let's now use this in designing Amat, et al...

NStox <- ncol( return_mat_Nodate )
LB = 0.01
UB = 0.25
meq = 1 # as only the first column of Amat is an equality (weight sum equals 1)
eq_UB = 0.6 #add constraints for eq and bonds
bond_UB = 0.4

#we also need a matrix for bonds and equities and then bind them to the amat
eq_const_mat<-  rbind(matrix(0, nrow = 9, ncol = 4),
                    -diag(4))


bond_const_mat <- rbind(matrix(0, nrow = 3, ncol = 6),
                     -diag(6),
                     matrix(0, nrow = 4, ncol = 6))

bvec <- c( 1, rep(LB, NStox), -rep(UB, NStox), -rep(bond_UB, 6), -rep(eq_UB, 4))
Amat <- cbind(1, diag(NStox), -diag(NStox), bond_const_mat, eq_const_mat )


#Now we can use Optim_foo from the practical

My_Weights <- 
  left_join(
  optim_foo(Type = "mv", mu, Sigma, LB= 0, UB =0.4, printmsg = F),
  optim_foo(Type = "minvol", mu, Sigma, LB= 0, UB =0.4, printmsg = F),
  by = c("Tickers")) %>% 
    left_join(.,optim_foo(Type = "erc", mu, Sigma, LB= 0, UB =0.4, printmsg = F),by = c("Tickers")) %>% 
      left_join(.,optim_foo(Type = "riskeff", mu, Sigma, LB= 0, UB =0.4, printmsg = F),by = c("Tickers"))
  

```

```{r}
#Need to make a reblance object


EOQ_datevec <- return_mat %>%
  select(date) %>%
  unique() %>%
  mutate(YM = format(date, "%Y%m")) %>%  # Format to include both year and month
  group_by(YM) %>%
  filter(lubridate::month(date) %in% c(1, 4, 7, 10)) %>%  # Filter for end of quarters
  summarise(date = last(date)) %>%
  pull(date)

#Use the function from the practical

Result36 <- 
EOQ_datevec %>% map_df(~Roll_optimizer(return_mat, EOQ_datevec = ., LookBackSel = 36)) 

kable(Result36 %>% head(13))

```

```{r}
#Lets get a bar plot of the weights overtime
bar_36_minvol<- Result36 %>% select(date, Tickers, minvol ) %>% spread(Tickers, minvol) %>% tbl_xts() %>% .[endpoints(.,'months')] %>% chart.StackedBar()
```

```{r}
bar_36_erc<- Result36 %>% select(date, Tickers, erc ) %>% spread(Tickers, erc) %>% tbl_xts() %>% .[endpoints(.,'months')] %>% chart.StackedBar()
```


```{r}
Result24 <- 
EOQ_datevec %>% map_df(~Roll_optimizer(return_mat, EOQ_datevec = ., LookBackSel = 24))

kable(Result24%>% head(13))
```

```{r}
Result12 <- 
EOQ_datevec %>% map_df(~Roll_optimizer(return_mat, EOQ_datevec = ., LookBackSel = 12))

kable(Result12%>% head(13))
```



\newpage

# References {-}

<div id="refs"></div>



