---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 2"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Wesley James Williams"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, South Africa" # First Author's Affiliation
Email1: "21691126\\@sun.ac.za" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Financial Econometrics 871"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 12pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Answers the Question of whether a manager should want to hedge against the ZAR or not.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(fmxdat)
library(PerformanceAnalytics)
library(tbl2xts)
Indexes <- read_rds("data/Cncy_Hedge_Assets.rds")
ZAR <- read_rds("data/Monthly_zar.rds")


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}
I start by replicating the figure given in the article. I then construct a hedged and un-hedged portfolio, calculate their three year rolling returns and standard deviation. Lastly, I compare the annualised returns and standard deviations over three different time periods to show that the results hold.

```{r}
#Lets start by constructing the porfolio, I want to optimise it using quadprog
# library(quadprog)
# #need to get rid of the dates to estimate Sigma
# return_mat_nodate <- data.matrix(Indexes[,-1])
# 
# library(RiskPortfolios)
# library(fitHeavyTail)
# #now use the RiskPortfolios or fitheavy tail packages to get sigma
# 
# HTT <- fitHeavyTail::fit_mvt(return_mat_nodate)
# Sigma <- HTT$cov
# mu <- HTT$mu
# 
# #make sure that the matrix is positive defninite
# Sigma <- as.matrix( Matrix::nearPD(Sigma)$mat)
# #now I am going to construct the amat and bvec to use quadprog to solve there are 4 assets where the first is global equity, the second is global bonds, the third is local equity and the last is local bonds therefore
# Amat <- matrix(c(1, 1, 0, 0, 1,
#                 1, 1, 0, 1, 0,
#                 1, 0, 1, 0, 1,
#                 1, 0, 1, 1, 0), 
#                  nrow = 4, 
#                  byrow = TRUE)
# bvec <- c(1, 0.3, 0.7, 0.4, 0.6 )
# 
# meq = 1 #only the first constraint must hold with equality
# w.opt <- 
#     quadprog::solve.QP(Dmat = Sigma,
#                             dvec = mu, 
#                             Amat = Amat, 
#                             bvec = bvec, 
#                             meq = meq)$solution
# w.opt
# 
# result.QP <- tibble(stocks = colnames(Sigma), weight = w.opt) 


# #That did not work so I am rarther going to use porfolio analytics to construct the optimal portfolio
# library(PortfolioAnalytics)
# library(tbl2xts)
# indexes <- Indexes %>% 
#     tbl_xts()
# 
# specifications <- portfolio.spec(colnames(indexes))
# specifications <- add.constraint(portfolio = specifications, type = "full_investment")
# specifications <- add.constraint(portfolio = specifications, type = "long_only")
# specifications <- add.constraint(portfolio = specifications, type = "group", groups = list(c(1,2)), group_max = 0.3, group_min = 0)
# specifications <- add.constraint(portfolio = specifications, type = "group", groups = list(c(3,4)), group_max = 0.7, group_min = 0)
# specifications <- add.constraint(portfolio = specifications, type = "group", groups = list(c(2,4)), group_max = 0.4, group_min = 0)
# specifications <- add.constraint(portfolio = specifications, type = "group", groups = list(c(1,3)), group_max = 0.6, group_min = 0)
# # specifications<- add.constraint(portfolio=specifications, type="box", min=0, max=c(0.18, 0.12, 0.42, 0.28))
# 
# rand_port <- random_portfolios(portfolio=specifications, permutations = 1000, rp_method ='sample')
# 
# optimal <- optimize.portfolio(R = indexes, portfolio = specifications, optimize_method = "random", rp = rand_port, trace = TRUE)

#This did not work either so i am just going to constrict the weighst by hand that fit the constraints eg offshore bonds can only be 30% of the 40% allocation to bonds

weights <- c(0.18, 0.12, 0.42, 0.28)

#now i am just adding a column with the weights and assuming it is an index rather than a portfolio so there are no rebalancing days
port_ret <- Indexes %>% 
    mutate(MSCI_ACWI_wt = 0.18) %>% 
    mutate(Bbg_Agg_wt = 0.12) %>% 
    mutate(J433_wt = 0.28) %>% 
    mutate(ALBI_wt= 0.28) %>% 
    mutate(port_ret =(MSCI_ACWI*MSCI_ACWI_wt)+ (Bbg_Agg*Bbg_Agg_wt)+ (J433*J433_wt)+(ALBI*ALBI_wt)) %>% 
    select(date, port_ret)

#Now I need to calculate the returns of the dollar rand exchange rate

ex_ret <- ZAR %>% 
    arrange(date) %>% 
    mutate(currency_ret = value/lag(value)-1) %>% 
    select(date, currency_ret) %>% 
    slice(-1)


#now we can join the two data frames
full_df <- port_ret %>% 
    left_join(., ex_ret, by = "date")
```

```{r Figure1, warning =  FALSE, fig.align = 'center', fig.cap = "Replication of Scatter plot \\label{Figure1}"}
#In order to get the percentages on the graph we need to identify how many observations are in each section where the top and bottom left quadrant we also need to consider the fee which appears to be about three percent
countingdf <- full_df %>% 
    na.omit() #This just gets rid of the nas
no_obs <- nrow(countingdf) #get the total number of observations so that we can actually get the percentages

#top right quandrant percentage calculation
TR_perc <- countingdf %>% 
    filter(port_ret >0) %>% 
    filter(currency_ret>0) %>% 
    nrow()/no_obs*100 
TR_perc <- round(TR_perc,0)

#botom right quadrant percentage calculation
BR_perc <- countingdf %>% 
    filter(port_ret <0) %>% 
    filter(currency_ret>0) %>% 
    nrow()/no_obs*100 
 BR_perc<-   round(BR_perc,0)

#top left quandrant percentage calculation
TL_perc <- countingdf %>% 
    filter(port_ret >0) %>% 
    filter(currency_ret<0) %>% 
    nrow()/no_obs*100
 TL_perc<- round(TL_perc,0)

#bottom left quandrant percentage calculation
BL_perc <- countingdf %>% 
    filter(port_ret <0) %>% 
    filter(currency_ret<0) %>% 
    nrow()/no_obs*100 
  BL_perc<-  round(BL_perc,0)

#Top left with fees quandrant percentage calculation
TLF_perc <- countingdf %>% 
    filter(port_ret >0) %>% 
    filter(currency_ret< -0.03) %>% 
    nrow()/no_obs*100 
 TLF_perc<-   round(TLF_perc,0)

#Bottom left with fees quandrant percentage calculation
BLF_perc <- countingdf %>% 
    filter(port_ret <0) %>% 
    filter(currency_ret< -0.03) %>% 
    nrow()/no_obs*100  
  BLF_perc<-  round(BLF_perc,0)

library(ggExtra)
library(glue)
#Now lets actually try and get the plot from ghost 
scatter_plot <- ggplot(full_df)+
    annotate("rect", xmin= 0, xmax = -Inf, ymin = 0, ymax = Inf, fill ="orange", alpha =0.5)+#top left quandrant
    annotate("rect", xmin= 0, xmax = -Inf, ymin = 0, ymax = -Inf, fill ="red", alpha =0.5)+#bottom left quandrant
    annotate("rect", xmin= 0, xmax = Inf, ymin = 0, ymax = Inf, fill ="green", alpha =0.5)+#top right quandrant
    annotate("rect", xmin= 0, xmax = Inf, ymin = 0, ymax = -Inf, fill ="green", alpha =0.2)+#bottom left quandrant
    geom_point(aes(x = currency_ret, y = port_ret), colour = "grey", alpha = 0.8)+
    geom_smooth(aes(x = currency_ret, y = port_ret),method = "lm")+
    geom_hline(yintercept = 0)+
    geom_vline(xintercept = 0)+
    geom_vline(xintercept = -0.03, linetype = "dashed")+
    geom_label(aes(x = -0.1, y = 0.1, label = "Hedge works but, amplifies Volatility"), color = "black", size = 2)+
    geom_label(aes(x = -0.1, y = -0.1, label = "Best case for hedge:\\ higher return lower volatility"), color = "black", size = 2) +
    geom_label(aes(x = 0.1, y = 0.1, label = "Hedge throws away returns"), color = "black", size = 2) +
    geom_label(aes(x = 0.1, y = -0.1, label = "Hedge removes currency cushion"), color = "black", size = 2)+
    geom_label(aes(x = -0.17, y = 0.17, label = glue("{TL_perc}%")), color = "black", size = 3)+
    geom_label(aes(x = -0.17, y = -0.17, label = glue("{BL_perc}%")), color = "black", size = 3)+
    geom_label(aes(x = 0.17, y = 0.17, label = glue("{TR_perc}%")), color = "black", size = 3)+
    geom_label(aes(x = 0.17, y = -0.17, label = glue("{BR_perc}%")), color = "black", size = 3)+
    geom_label(aes(x = -0.17, y = 0.17, label = glue("{TL_perc}%")), color = "black", size = 3)+
    geom_label(aes(x = -0.05, y = -0.17, label = glue("{BLF_perc}%")), color = "black", size = 3)+
    geom_label(aes(x = -0.05, y = 0.17, label = glue("{TLF_perc}%")), color = "black", size = 3)+

    labs(title = "Scatter Plot of USD/ZAR and Portfolio returns ", x = "USD-ZAR Returns", y = "60-40 Local-Global Returns")+
    lims(x = c(-0.2, 0.2), y = c(-0.2, 0.2)) +  # Set axis limits
    theme_bw()



scatter_plot_density <- ggMarginal(scatter_plot, type = "density", margins = "both", fill = "blue")

scatter_plot_density

```












# Volatility analysis
```{r}

#Lets use the fee converter again assuming that there are fees for hedging assuming the same three percent as above
 feeconverter <- function(x, Ann_Level) (1+x)^(1/Ann_Level)-1

#The hedged return is exactly the return of the global assets less the fee to hedge
hedged<- Indexes %>% 
    mutate(MSCI_ACWI_wt = 0.18) %>% 
    mutate(Bbg_Agg_wt = 0.12) %>% 
    mutate(J433_wt = 0.28) %>% 
    mutate(ALBI_wt= 0.28) %>% 
    mutate(hedged_ret =(MSCI_ACWI*MSCI_ACWI_wt)+ (Bbg_Agg*Bbg_Agg_wt)+ (J433*J433_wt)+(ALBI*ALBI_wt) - feeconverter(300*1e-4, Ann_Level = 12)) %>% 
    select(date, hedged_ret)

unhedged <- Indexes %>% 
    left_join(., ex_ret, by ="date") %>% 
    filter(!is.na(currency_ret)) %>% 
    mutate(MSCI_ACWI_wt = 0.18) %>% 
    mutate(Bbg_Agg_wt = 0.12) %>% 
    mutate(J433_wt = 0.28) %>% 
    mutate(ALBI_wt= 0.28) %>% 
    mutate(unhedged_ret =((MSCI_ACWI*MSCI_ACWI_wt)+ (Bbg_Agg*Bbg_Agg_wt))*currency_ret + (J433*J433_wt)+(ALBI*ALBI_wt)) %>% #here the global assets are subject to the volatility of the rand
    select(date, unhedged_ret)

#Now we can join the dfs so we can compare the returns and the volatility
hedged_comp_df <-
    left_join(unhedged, hedged, by = "date") %>% 
    rename("Hedged"= "hedged_ret", "Unhedged"= "unhedged_ret")

#Lets get the annulised returns for both portfolios
#Start by getting tidy data
tidy_hedged <-hedged_comp_df
```


```{r Figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Rolling 2 year Annualised Returns\\label{Figure2}"}
#Now lets plot the rollinf returns and SD
#Let's again use the RcppRoll package agin to get annualised reterns and volatility
library(RcppRoll)

roll_ret_hedge <- hedged_comp_df %>% 
    gather(Type, ret, -date) %>% #here type refers to whether it is hedged or not
    group_by(Type) %>% 
    mutate(RollRets = RcppRoll::roll_prod(1 + ret, 24, fill = NA, 
    align = "right")^(12/24) - 1) %>% 
    group_by(date) %>% filter(any(!is.na(RollRets))) %>% 
ungroup()

roll_ret_hedge_plot<- 
roll_ret_hedge %>% 
ggplot() + 
geom_line(aes(date, RollRets, color = Type), alpha = 0.7, 
    size = 1) + 
labs(title = " Rolling 2 Year Annualized Returns", 
    subtitle = "", x = "", y = "Rolling 2 year Returns "
    ) + fmxdat::theme_fmx()

roll_ret_hedge_plot
```
Figure \ref{Figure2} incorporates the fee identified in the study and in Figure \ref{Figure1}. Once the fee has been accounted for it is clear to see the that unhedged portfolio almost always outperforms it's hedged counterpart.
```{r Figure3, warning =  FALSE, fig.align = 'center', fig.cap = "Rolling 2 year Annualised SD\\label{Figure3}"}
#Now lets get the rolling sd as a measure of volatility

roll_SD_hedge <-  hedged_comp_df %>% 
    gather(Type, ret, -date) %>% 
    group_by(Type) %>%
    mutate(RollSD = RcppRoll::roll_sd(1 + ret, 36, fill = NA, align = "right") * 
    sqrt(12)) %>% 
filter(!is.na(RollSD))

roll_SD_hedge_plot<- roll_SD_hedge %>% 
ggplot() + 
geom_line(aes(date, RollSD, color = Type), alpha = 0.7, size = 1.25) + 
    
labs(title = "Rolling 3 Year Annualized SD ", x = "", y = "Rolling 2 year SD") + theme_fmx()

roll_SD_hedge_plot
```
If the returns comparison was not convincing enough the comparison of a two year rolling SD paints an even clearer picture. Throughout the entire sample period the Hedged portfolio is more risky. Figures \ref{Figure4} and \ref{Figure5} only strengthen this argument to show that the results are strong irrespective of the lookback period. Finally the table at the end of the question calculates the correlations of both portfolios to the USD/ZAR exchange rate and finds that hedged portfolio is more negatively correlated to the USD/ZAR exchange rate. This confirms the existence of the paradox in volatility in that negatively correlated assets may produce portfolio volatilities that
are lower than the sum of its parts.
```{r Figure4, warning =  FALSE, fig.align = 'center', fig.cap = "Rolling Returns over time\\label{Figure4}"}
#Lets give that table a crack
#Lets get the annulised returns for both portfolios
#Start by getting tidy data
tidy_hedged <-hedged_comp_df %>% 
    gather(Type, ret, -date) %>% 
    tbl_xts(., cols_to_xts = ret, spread_by = Type)

#Now lets use the performance analytics package to get the annulized returns and std devs following the practical 

hedge_plot <- 
    bind_rows(
        tidy_hedged %>% tail(12) %>% PerformanceAnalytics::Return.annualized(., scale = 12) %>% data.frame() %>% mutate(Freq = "A"),
        tidy_hedged %>% tail(36) %>% PerformanceAnalytics::Return.annualized(., scale = 12) %>% data.frame() %>% mutate(Freq = "B"),
        tidy_hedged %>% tail(60) %>% PerformanceAnalytics::Return.annualized(., scale = 12) %>% data.frame() %>% mutate(Freq = "C")
    )%>% data.frame() %>% gather(Type, mu, -Freq)
to_string <- as_labeller(c(`A` = "1 Year", `B` = "3 Years", `C` = "5 Years"))

g <- hedge_plot %>% 
ggplot() + 
    
  geom_bar( aes(Type, mu, fill = Type), stat="identity") + 
    
  facet_wrap(~Freq, labeller = to_string, nrow = 1) + 
    
  labs(x = "", y = "Returns (Ann.)" )+
    theme_fmx()
g
```
```{r Figure5, warning =  FALSE, fig.align = 'center', fig.cap = "Rolling SD over time\\label{Figure5}"}
#Now I plot a similar graph instead looking at the volatility
hedge_plot_SD <- 
    bind_rows(
        tidy_hedged %>% tail(12) %>% PerformanceAnalytics::StdDev.annualized(., scale = 12) %>% data.frame() %>% mutate(Freq = "A"),
        tidy_hedged %>% tail(36) %>% PerformanceAnalytics::StdDev.annualized(., scale = 12) %>% data.frame() %>% mutate(Freq = "B"),
        tidy_hedged %>% tail(60) %>% PerformanceAnalytics::StdDev.annualized(., scale = 12) %>% data.frame() %>% mutate(Freq = "C")
    )%>% data.frame() %>% gather(Type, mu, -Freq)
to_string <- as_labeller(c(`A` = "1 Year", `B` = "3 Years", `C` = "5 Years"))

Vol_annulised <- hedge_plot_SD %>% 
ggplot() + 
    
  geom_bar( aes(Type, mu, fill = Type), stat="identity") + 
    
  facet_wrap(~Freq, labeller = to_string, nrow = 1) + 
    
  labs(x = "", y = "Vol (Ann.)" )+
    theme_fmx()
Vol_annulised
```
```{r}
#Lastly I just want to plot the correlations between exchange rate and the portfolios
rho_hedge<- hedged_comp_df %>% 
    left_join(., ex_ret, by = "date") %>% 
    mutate(hedge_rho = cor(Hedged, currency_ret)) %>% 
    mutate(unhedged_rho = cor(Unhedged, currency_ret)) %>% 
    select(date, hedge_rho, unhedged_rho) %>% 
    rename("Hedged"= "hedge_rho", "Unhedged" = "unhedged_rho") %>% 
    gather(Type, Correlation, -date) %>% 
    group_by(Type) %>% 
    summarise(Correlation= mean(Correlation))


kableExtra::kable(rho_hedge)

```




\newpage

# References {-}

<div id="refs"></div>




